Climate indicators

### 2023-02-22 DRAFT_climate_indicators.Rmd
plot time aggregation results

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)

dir <- substr(getwd(), 1,2)

@@

@@

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stars)
library(sf)
library(tmap)
library(lubridate)
library(ggpubr)
dir <- substr(getwd(), 1,2)

@@

Let me introduce some differences to Attribute_A between these two dates.
```{r}
x_aug$Attribute_A[,,,2] <- x_aug$Attribute_A[,,,1]*4
```

@@

```{r, fig.cap="Plotting the dummy data showing Attribute_A for the two dates as small maps, and a larger map showing the mean for year 2018"}
ggarrange(
ggplot() + 
  geom_stars(data = x_aug) +
  coord_equal() +
  facet_wrap(~time) +
  theme_void() +
  scale_fill_viridis_c(option = "D") +  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)),

ggplot() + 
  geom_stars(data = x_summerMean_v2) +
  coord_equal() +
  facet_wrap(~time) +
  theme_void() +
  scale_fill_viridis_c(option = "D") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0))
)
```
